### 2021-05-24 article/article.tex
update

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism}
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

@@

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real. In Fig.~\ref{fig:flux_ratio}, we study
the flux ratio arising from the introduction of the NSI parameter $\emt$. Fig.~\ref{fig:Pmm_asymmetry} shows the difference $P_{\mu\mu}(\emt>0) - P_{\mu\mu}(\emt<0)$ in the low \si{\GeV} energy range. 
%TODO: maybe plot P_NSI - P_SI instead.

\section{Detector formalism}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation for varying density. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor of $\sim \sqrt{10}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios
In IceCube, we will only consider muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor $\sim 10$, we now have deficiencies in the order of $\sim \sqrt{10}$.

@@

\subsection{IceCube}\label{ch:ICmethod}
We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ coincide with $\zreco$ for our study~\cite{IC2020}.

@@

\section{Results}
In this section, we present the results from the experiments alone, as well as jointly. 
\subsection{Methodology}\label{sec:method}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

@@

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. We consider best, normal, and worst-case scenarios in IceCube assuming
$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead assume $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
{\renewcommand{\arraystretch}{1.2}
\begin{table}
   \begin{tabular}{lccc}
      \hline \hline
      Experiment & Worst case & Normal case & Best case \\
      \hline
      IceCube & $15\%$ & $10\%$ & $5\%$ \\
      PINGU & $5\%$ & $3\%$ & $0\%$ \\
      \hline \hline
   \end{tabular}
   \caption{Definition of the worst and best case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
\end{table}

\subsection{Constraining the NSI parameters}
First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D}. We record the 
confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.

\begin{figure}
   \begin{center}
      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters other than the one shown are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
   \end{center}
\end{figure}
%TODO: dont put pingu and dc side by side since pingu is generated.. include 3sigma if possible?

We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:joint_3D}, especially in $\emt$ and $\eet$.%TODO: make better
We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
%TODO: check that this is what is plotted.
$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i.e. after reconstruction? 
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$. DeepCore on the other hand, 
has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
$\emt$ asymmetry stems from the lower statistics for $\emt< 0 $ at probability level, which is then preserved through the flux and finally the reconstruction. %TODO: fill more conclusion?

@@

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}\label{eq:joint_chisq}
    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
\newpage

>>>>

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism of non-standard interactions}
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions not considered in the Standard Model.
We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

@@

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real.

\subsection{Probability effects in the GeV range}
In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
the three different effects in Fig.~\ref{fig:nsi_probs}.

Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
   \caption{The three different effects that the off-diagonal NSI parameters have in the \si{\GeV} range.}\label{fig:nsi_probs}
\end{figure}

\section{Detector formalism}
The neutrino flux at the detector is calculated by propagating the atmospheric neutrino flux from Honda et al~\cite{hondapaper} through the Earth by solving the 
Schrödinger equation with the Hamiltonian from Eq.~\ref{eq:H_NSI}. The Earth density profile is taken from the PREM~\cite{PREM}. The baseline for a given trajectory is determined using an average neutrino
production height of 15 km and an Earth radius of 6371 km. The propagation does not include neutrino absorption.
%TODO: add more here? are there more effects than just absoption missing? justify absorption missing?

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux for flavor $\beta$ at detector level as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
is a energy-independent flux deficiency with a factor in the order of $\sim 10^{0.5}$ from core-crossing neutrinos within a zenith range of $\ztrue < -0.87$. DeepCore on the other hand, 
is exposed to multiple fringes of flux surpluses with a factor in the order of $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensitive IceCube deficiency.
%TODO: check values above after final plot of flux ratios
In IceCube, we will only consider muon track events. Thus, we have to resort to the DeepCore/PINGU detector alone for the $\nu_e$ and $\nu_\tau$ fluxes.
Here we see a somewhat weaker signal, this time a zenith-independent deficiency. Where we earlier had surpluses with a factor in the order of $\sim 10$, we now have deficiencies in the order of $\sim 10^{0.5}$.

@@

\subsection{IceCube}\label{ch:ICmethod}
We obtain the data from the IC-86 sterile data release~\cite{IC2020}, which was collected over 8 years. The event rate for each bin reads
\begin{align}\label{eq:ICevents}
   N_{ij} &= T\sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r \int_0^\pi R(\theta^r,\theta^t) \dd \cos{\theta^t} \int_0^\infty \phi_\beta^\text{det}(E^t,\theta^t)  A^\text{eff}(E^t) R(E^r,E^t) 
   \dd E^t\,,
\end{align}
where $T$ is the live time of the detector, and $A^\text{eff}$ its effective area averaged over the flavors $\beta$ from~\cite{ICaeff}. $R(x^r,x^t)$ is a resolution function, 
which is responsible for the smearing between the reconstructed and true parameters $x^r$ and $x^t$, respectively. We assume a log-normal distribution, giving it the form 
\begin{align}
    R(x^r, x^t) = \frac{1}{\sqrt{2\pi} \sigma_{x^r}x^r} \exp\left[-\frac{(\log x^r-\mu(x^t))^2}{2\sigma_{x^r}^2}\right]\,.
\end{align}
However, the energy reconstruction is biased, which means that we don't assume that $\mu(E^t) =E^r$~\cite{weaverEvidenceAstrophysicalMuon}. 
To model this relationship between $\Etrue$ and $\Ereco$, we train a Gaussian process regressor on the IC-86 Monte Carlo dataset from~\cite{IC2016}, from which
we can extract a predicted mean and standard deviation for a given $E^{reco}$. We then take the $\Etrue$ points of the 99th percentile of each distribution to obtain
the limits over which to integrate. We take the angular resolution function to be identically unity since the angle resolution in IceCube for track-like 
events is less than $\SI{2}{\degree}$, making $\ztrue$ practically coincide with $\zreco$ for our study~\cite{IC2020}.

@@

\section{Results}
In this section, we present the results from the experiments alone, as well as jointly. 
\subsection{Methodology}\label{sec:method}
%TODO a sentence about simplicity
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. 
We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

@@

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$.
We consider best, normal, and worst-case scenarios in IceCube using
$f=5\%$, $7.5\%$, and $f=15\%$ respectively. For PINGU, we use the same form but instead use $f=0\%$, $3\%$, and $f=5\%$. %TODO: maybe source/justification for these values?
For DeepCore, we use the provided systematic error distribution which accounts for uncertainties in the finite MC statistics and the data-driven 
muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
{\renewcommand{\arraystretch}{1.2}
\begin{table}
   \begin{tabular}{lccc}
      \hline \hline
      Experiment & Best case & Baseline & Worst case \\
      \hline
      IceCube & $5\%$ & $10\%$ & $15\%$ \\
      PINGU & $0\%$ & $3\%$ & $5\%$ \\
      \hline \hline
   \end{tabular}
   \caption{Definition of the best, baseline, and worst case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
   We do not consider different DeepCore scenarios because her systematic error distribution is already provided in the data release~\cite{DC2019data}.}\label{table:syst_errors}
\end{table}

\subsection{Constraining the NSI parameters}
First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:joint_3D_NO}. We record the 
confidence levels in Table~\ref{table:IC_DC_results} and Table~\ref{table:PINGU_joint_results}, and best-fit points in Table~\ref{table:bestfit}.

\begin{figure}
   \begin{center}
      \includegraphics[width=0.6\textwidth]{figures/joint_3D_NO.pdf}
      \caption{PINGU and DeepCore best-case scenario, with their joint $\Delta \chi^2$ in black. $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.6\textwidth]{figures/PID_3D_emt.pdf}
      \caption{$\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.}\label{fig:IC_3D}
   \end{center}
\end{figure}

We see asymmetrical shapes in the $\Delta \chi^2$ plots in Fig.~\ref{fig:3D_NO}, especially in $\emt$ and $\eet$.%TODO: make better
We investigate this for $\emt$ by plotting the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
%TODO: check that this is what is plotted.
$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}. Muon events are the most abundant, and it suffices to study $P_{\mu\mu}$ to explain the $\emt$ asymmetry. 
We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratio}, this muon survival abundance 
is indeed preserved at flux level. So the flux for $\emt>0$ is higher than the flux for $\emt<0$. Is this still true at event level, i.e. after reconstruction? 
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$. DeepCore on the other hand, 
has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side. Thus, we conclude that the DeepCore
$\emt$ asymmetry stems from the lower statistics for $\emt< 0 $ at probability level, which is then preserved through the flux and finally the reconstruction. %TODO: fill more conclusion?

@@

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}

For the joint analysis, we follow the parameter goodness-of-fit prescription~\cite{maltoni2003} and construct the joint $\chi^2$ as 
\begin{align}\label{eq:joint_chisq}
    \chi^2_\text{joint} = \sum_\text{exp}\chi^2_\text{exp} - \chi^2_\text{exp,min}\,
\end{align}
with test statistic $\chi^2_\text{joint,min}$. The $\Delta \chi^2_\text{joint}$ is then $\Delta \chi^2_\text{joint} = \chi^2_\text{joint} - \chi^2_\text{joint,min}$.
The results are shown in Fig.~\ref{fig:joint_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}.
Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU,
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
\newpage
